Pillar 1 - Sequential Pattern Mining

### 2019-06-05 Trials/Pillar 1 - Sequential Pattern Mining.Rmd
create folder for trials

```{r constants}
course_all  <- unique(d_transcript_informative$`Course ID` )
student_all <- unique(d_transcript_informative$`Student ID`)
n_students  <- length(student_all)

@@

# Probability of taking / failing / obtaining of low grade a course
d_support$TPH <- d_transcript_informative %>%

@@

```{r d_support G}
d_support$G <- d_transcript_informative %>%

@@

## taken_PF_HL
```{r taken_PF_HL}
d_transactions$taken_PF_HL <- d_transcript_informative %>%

@@

  mutate(
    course_so_far  = course_current %>% accumulate(union),
    course_past    = course_so_far  %>% lag(default = NA_character_),
    course_not_yet = course_past    %>% map(~ setdiff(course_all, .) %>% paste_("not"))
    ) %>%

>>>>

```{r constants}
course_all  <- unique(d_transcript_elective$`Course ID` )
student_all <- unique(d_transcript_elective$`Student ID`)
n_students  <- length(student_all)

@@

# Probability of taking / failing / obtaining of low grade a course
d_support$TPH <- d_transcript_elective %>%

@@

```{r d_support G}
d_support$G <- d_transcript_elective %>%

@@

## taken_PF_HL
```{r taken_PF_HL}
d_transactions$taken_PF_HL <- d_transcript_elective %>%

@@

  mutate(
    course_so_far  = course_current %>% purrr::accumulate(union),
    course_past    = course_so_far  %>% lag(default = NA_character_),
    course_not_yet = course_past    %>% map(~ setdiff(course_all, .) %>% paste_("not"))
    ) %>%
